Seismic Hazard Estimation of Northern Iran Using Smoothed Seismicity

### 2016-07-08 conclusions.tex
finalizing results section
finished... I think

\section{Conclusion}
The result of a new probabilistic seismic hazard assessment for northern Iran using updated seismic catalogs is provided. Seismic hazard is evaluated over entire three regions (Azerbaijan, Alboz, Kopeh-Dagh) as well as part of Central and Zagros tectonic seismic regions using the smoothed background seismicity. In order to determine the seismic hazard in North Iran, different studies have been done. These studies are based on defining faults as a seismic source model. Using faults as a seismic source model could result in accurate values in case the faults are precisely determined. There are considerable uncertainties on fault characteristic, specially on fault length. Instead of using faults as a seismic source, we consider each earthquake event as a point source in the model. We reduce the uncertainty in earthquake location by smoothing the number of earthquake in adjacent cells. We defined models based on considering the whole North Iran as a uniform seismic tectonic regions and 5 different seismic tectonic regions. The differences in catalog completeness, b value, and maximum magnitude of earthquake in these two models resulted in different results. This indicate the idea that dividing regions into subregions is necessary in order to be able to get accurate results. The result are also sensitive to the minimum magnitude. The structures built according to engineering code are supposed to withstand the earthquake with magnitude 5 at the reasonable distance. However, closer $M_w > 4.5$ for those structures and also older masonry structures could cause structural damage. A combination of two models $(M_w > 4.5, M_w>5)$ in each city based on number of engineering and old masonry structures will provide more accurate results. The results are provided for mean peak horizontal acceleration in bedrock. The ground acceleration in soil deposits and inside basin will be bigger than the provided values. This model reduce the epistemic uncertainty regarding the recognizing faults and earthquake location. Combination of this model with a study based on using faults will increase the values for existing non-active seismic fault regions.

>>>>

\section{Concluding Remarks}

We present results from a comprehensive seismic hazard analysis for the region of northern Iran based on a smoothed seismicity approach, including regional maps of expected peak ground accelerations for different seismic-zonation models and magnitude thresholds. In particular, we calculated the hazard for the region of interest using two basic models, a five-seismic zone regions model and a uniform seismic zone model. Our calculations yield results similar to those of other studies but offer a more complete picture than previous hazard analysis due to the usage of a more complete catalog and inclusion of low-magnitude events. In our analysis we found it convenient to combine both the regional and uniform models as a mean to consider the epistemic uncertainty intrinsic to the subjective choice of models and seismic zones. Such a combination yielded hazard maps that adjusted better to the visual interpretation of the historical and instrumental seismicity observed in the region of interest, and the to the location of known seismically active faults. While no one model can be deemed more appropriate than others, we believe our results constitute a positive contribution to the understanding of seismic hazard in the region, especially for rural ares which are not the subject of specialized hazard studies such as those conducted for major urban areas. Future work to improve the results presented here should consider alternative attenuation relationships, especially for estimating other ground motion parameters such as response spectral accelerations for different periods and site effects.

% ---------
% OLD STUFF
% ---------

% The result of a new probabilistic seismic hazard assessment for northern Iran using updated seismic catalogs is provided. Seismic hazard is evaluated over entire three regions (Azerbaijan, Alboz, Kopeh-Dagh) as well as part of Central and Zagros tectonic seismic regions using the smoothed background seismicity. In order to determine the seismic hazard in North Iran, different studies have been done. These studies are based on defining faults as a seismic source model. Using faults as a seismic source model could result in accurate values in case the faults are precisely determined. There are considerable uncertainties on fault characteristic, specially on fault length. Instead of using faults as a seismic source, we consider each earthquake event as a point source in the model. We reduce the uncertainty in earthquake location by smoothing the number of earthquake in adjacent cells. We defined models based on considering the whole North Iran as a uniform seismic tectonic regions and 5 different seismic tectonic regions. The differences in catalog completeness, b value, and maximum magnitude of earthquake in these two models resulted in different results. This indicate the idea that dividing regions into subregions is necessary in order to be able to get accurate results. The result are also sensitive to the minimum magnitude. The structures built according to engineering code are supposed to withstand the earthquake with magnitude 5 at the reasonable distance. However, closer $M_w > 4.5$ for those structures and also older masonry structures could cause structural damage. A combination of two models $(M_w > 4.5, M_w>5)$ in each city based on number of engineering and old masonry structures will provide more accurate results. The results are provided for mean peak horizontal acceleration in bedrock. The ground acceleration in soil deposits and inside basin will be bigger than the provided values. This model reduce the epistemic uncertainty regarding the recognizing faults and earthquake location. Combination of this model with a study based on using faults will increase the values for existing non-active seismic fault regions.

### 2016-07-08 results.tex
finished... I think

Table \ref{tab:pga} shows a condensed version of these comparisons between our results and those of other previous studies for selected cities in northern Iran. In addition, we also looked into the more complete picture of the annual probabilities of exceedance as functions of PGA for six cities (all the same as in Table \ref{tab:pga} except Rasht). This is shown in Fig.~\ref{fig:hazardcurve} for the four basic models considered before, namely R5.5, R6.5, U5.5 and U6.5, each also including upper and lower ranges of one standard deviation. These hazard curves exemplify again the differences between the R and U models, which are more prominent in the northwest cities of Tabriz and Ardabil, where the U models yield higher expected values of PGA for any given annual probability of exceedance. Minor differences are also present in the central cities of Karaj and Tehran, whereas the cities of Urmia and Mashhad in the Zagros and Kopeh Dagh seismic zones present similar hazard levels between the two models (R and U). This is consistent with our previous observations regarding Figs.~\ref{fig:pga}, \ref{fig:pgadiff} and \ref{fig:pgaavgs}.

Last, we pay additional attention to the capital city of Tehran and compare hazard...

~\\
* * *
\\

>>>>

Table \ref{tab:pga} shows a condensed version of these comparisons between our results and those of other previous studies for selected cities in northern Iran. As mentioned before, overall, our results are close or within the ranges from most studies. The only noticeable exceptions are the results of \citet{Golara2014}, whose expected PGA values are significantly higher the rest, especially in the cities of Tabriz, Karaj, Tehran and Mashhad. This is likely due to the authors working with mower magnitude thresholds (not clearly reported) than other studies where hazard is usually estimated based on earthquake magnitudes exceeding $M_w > 5$. Although not included here for brevity we also computed expected PGA values for a magnitude threshold of $M_w$ 4.5 and 5.0. We found the former case to yield results closer to those of \citet{Golara2014}, but not to the other studies. Using lower magnitude thresholds may be of relevance if evaluating poorly constructed and unreinforced buildings vulnerable to low-to-moderate magnitude earthquakes.

Following the comparisons shown in Table \ref{tab:pga}, we looked into the more complete picture of the annual probabilities of exceedance as functions of PGA. The results are shown in Fig.~\ref{fig:hazardcurve} for six of the main cities in northern Iran considering the four basic models R5.5, R6.5, U5.5 and U6.5. In each case we also show $\pm 1$ standard deviation (shaded ranges). These hazard curves exemplify again the differences between the R and U models, which are more prominent in the northwest cities of Tabriz and Ardabil, where the U models yield higher expected values of PGA for any given annual probability of exceedance. Minor differences are also present in the results of the central cities of Karaj and Tehran, whereas for the cities of Urmia and Mashhad in the Zagros and Kopeh Dagh seismic zones, the R and U models yield similar hazard levels. This is consistent with our previous observations regarding Figs.~\ref{fig:pga}, \ref{fig:pgadiff} and \ref{fig:pgaavgs}.

Last, we put additional attention on the results for the capital city of Tehran. We compare hazard curves obtained in this study against those computed by \citet{Ghodrati2003} and \citet{Boostan2015}. Our results are similar to those obtained by \citet{Ghodrati2003} between 0.4 and 0.8 g (corresponding to annual probabilities of exceedance between $10^{-5}$ and $10^{-3}$), but we obtain lower probabilities for the ground motion amplitudes between 0.1 and 0.4 g, and higher probabilities for very low ($<0.1$ g) and much higher PGA ($>0.8$ g) values. These differences with \citet{Ghodrati2003}, nonetheless, are still within our levels of uncertainty. A similar interpretation can be made for the comparison with \citet{Boostan2015} for low PGA values ($<0.4$ g), but the trajectory of their hazard curve suggests much higher probabilities of exceeding PGA values above 0.6 g, which is contrary to our findings.
